\emph{icepack}: a novel glacier flow modeling package

### 2020-11-11 icepack.tex
Add synthetic ice shelf figure

\subsection{Synthetic ice shelf with damage transport}

We simulated the evolution of a synthetic ice shelf towards steady state and coupled it with the damage transport model described in \S\ref{sec:damage-transport}.
The geometry of the ice shelf consists of the intersection of two circles, one with a larger radius and offset center, designed to roughly mimic the shape and size of real ice shelves.
The radius of the whole shelf is 200km.
Four ice streams flow into the shelf with varying speeds and a prescribed inflow thickness.
In the first phase of the experiment, the ice shelf is propagated to steady state without damage for 200 years.
After this time interval, the flux imbalance is less than 1\% of the influx.
In the second phase, damage transport is turned on and coupled to the ice velocity.
An interesting feature to observed in the approximate equilibrium damage field is that the highest values occur between the streams and not within them.
Additionally, the spacing between the streams changes as a result of adding damage.
The final ice thickness, velocity, strain rate, and damage are shown in figure \textcolor{red}{ZZZ}.

>>>>

\subsection{Synthetic ice shelf}

\begin{figure}[h]
    \includegraphics[width=0.95\linewidth]{demos/gibbous/damage.png}
    \caption{Results of ice shelf damage simulation: (a) ice velocity, (b) change in ice speed with and without damage, (c) thickness, and (d) damage field.}
    \label{fig:damage}
\end{figure}

We simulated the evolution of a synthetic ice shelf towards steady state and coupled it with the damage transport model described in \S\ref{sec:damage-transport}.
The geometry of the ice shelf consists of the intersection of two circles, one with a larger radius and offset center, designed to roughly mimic the shape and size of real ice shelves.
The radius of the whole shelf is 200km.
Four ice streams flow into the shelf with varying speeds and a prescribed inflow thickness.
In the first phase of the experiment, the ice shelf is propagated to steady state without damage for 200 years.
After this time interval, the flux imbalance is less than 1\% of the influx.
In the second phase, damage transport is turned on and coupled to the ice velocity.
An interesting feature to observed in the approximate equilibrium damage field is that the highest values occur between the streams and not within them.
Additionally, the spacing between the streams changes as a result of adding damage.
The final ice thickness, velocity, strain rate, and damage are shown in figure \ref{fig:damage}.
